Cluster Paper

### 2015-04-06 ms.tex
added oii luminosity section

\section{AARDVARK SIMULATION}
\editorial{Waiting to get a look at what Casey comes up with for the proposal we are supposedly writing. If he does a decent job then I'll try to expand it a bit and fill out this section.}

@@

\subsection{Mock Observations}
\editorial{Here we need to talk about about how we set up the observations to look like what we think the HETDEX survey will see. It should be more techincal than the general discussion about what the survey hopes to accomplish, that'll go in the intro. A zoomed figure showing the tiling footprints would be appropriate.}

@@

>>>>

\section{AARDVARK SIMULATION}
\editorial{Waiting to get a look at what Casey comes up with for the proposal we are supposedly writing. If he does a decent job then I'll try to expand it a bit and fill out this section.}
\begin{figure} 
	\includegraphics[width=0.49\textwidth]{surveyArea.pdf} 
	\caption{A polar azimuthal equidistant projection of the southern sky showing the sky area (approximately a quarter of the sky) covered by the Aardvark Simulations. Concentric circles are lines of constant declination, 10 to $-80\degree$ in $10\degree$ increments. Radial lines are lines of constant right ascension. Opaqueness of the region indicates the overlap of catalog tiles (see text for details).} 
	\label{fig:survey area} 
\end{figure}

@@

\subsection{Mock Observations}
\editorial{Here we need to talk about about how we set up the observations to look like what we think the HETDEX survey will see. It should be more technical than the general discussion about what the survey hopes to accomplish, that'll go in the intro. A zoomed figure showing the tiling footprints would be appropriate.}

\begin{figure} 
	\includegraphics[width=0.49\textwidth]{f01.pdf} 
	\caption{} \label{fig:ifu layout} 
\end{figure}

@@

\subsection{\ion{O}{ii} Luminosity}

HETDEX is designed to detect Lyman-$\alpha$ at redshift two. That allows us to detect \ion{O}{ii} emitters to $z\sim 0.49$. The catalog does not provide \ion{O}{ii} luminosities so we must assign them empirically. We use 177107 galaxies from the Sloan Digital Sky Survey (SDSS) Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$. Galaxies are selected which have no redshift warning and have an \ion{O}{ii} flux five times greater than the \ion{O}{ii} flux error.

\begin{figure} 
	\includegraphics[width=0.49\textwidth]{oii_sdss.pdf} 
	\caption{} \label{fig:oii sdss} 
\end{figure}

We place each SDSS galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}. To assign an \ion{O}{ii} luminosity to each galaxy in our catalog we place the galaxies on the same and select all SDSS galaxies in a small 2D bin around the galaxy. We extract all of the SDSS galaxies inside that bin and create a histogram of their \ion{O}{ii} luminosities. Using a slice sampling technique we assign the catalog galaxy an \ion{O}{ii} luminosity based on the distribution of SDSS galaxies extracted.

For catalog galaxies which are placed on the CMD near no, or very few ($n<3$) galaxies we assign it zero \ion{O}{ii} luminosity or the mean luminosity, respectively.
